---
title: "Code for Lin et al., 2021"
author: "CP Lin"
date: "2021/6/12"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r setup}
library(INLA)
# load("~/Rstudio/COVID/data_for_influenza_v26_trial.RData")
# rm(list=setdiff(ls(),c("train0_combine","train0_2020","abc","cf_2016","cf_2018","cf_2019")))
```

## prepare the data variable
```{r}
## read the raw data file from flu express
dat0 <- read.csv("dat0.csv",header = T)  
dat0$date = as.Date(dat0$ï..date, origin = "1899-12-30")


### prepare "train0_combine"
train0 = data.frame(dat0$date,dat0$real.flu.case)
names(train0) = c("dates","I")

train0_2016 = train0[35:62,] ## weekly
train0_2016$yminus_one = train0$I[34:61]
train0_2016$N = 7000000 - sum(train0$I[6:34])/0.2
train0_2016$cumsum_yminus = cumsum(train0_2016$yminus_one)

train0_2018 = train0[140:161,] ## weekly
train0_2018$yminus_one = train0$I[139:160]
train0_2018$N = 7000000 - sum(train0$I[105:139])/0.2
train0_2018$cumsum_yminus = cumsum(train0_2018$yminus_one)

train0_2019 = train0[185:210,] ## weekly
train0_2019$yminus_one = train0$I[184:209]
train0_2019$N = 7000000 - sum(train0$I[160:184])/0.2
train0_2019$cumsum_yminus = cumsum(train0_2019$yminus_one)

train0_2020 = train0[242:255,]  ## weekly
train0_2020$yminus_one = train0$I[241:254]
train0_2020$N = 7000000 - sum(train0$I[212:241])/0.2
train0_2020$cumsum_yminus = cumsum(train0_2020$yminus_one)

train0_2016$gp = 2016
train0_2018$gp = 2018
train0_2019$gp = 2019
train0_2020$gp = 2020

train0_combine = data.frame(rbind(train0_2016,train0_2018,train0_2019, train0_2020[1:8,]))

train0_combine$gp2016 = train0_combine$gp==2016
train0_combine$gp2018 = train0_combine$gp==2018
train0_combine$gp2019 = train0_combine$gp==2019
train0_combine$gp2020 = train0_combine$gp==2020

train0_combine$logI = log(train0_combine$I)
train0_combine$logyminus_one = log(train0_combine$yminus_one)
train0_combine$cumsum_yminus_over_N = train0_combine$cumsum_yminus/train0_combine$N


### prepare "train0_2020"
train0_2020$logI = log(train0_2020$I)
train0_2020$logyminus_one = log(train0_2020$yminus_one)
train0_2020$cumsum_yminus_over_N = train0_2020$cumsum_yminus/train0_2020$N


##########################  prepare correction factor for reporting rate from severe cases
cf_2016 = sum(dat0$severe_case[match(train0_2016$dates,dat0$date)])/sum(train0_2016$I) ## 2016
cf_2018 = sum(dat0$severe_case[match(train0_2018$dates,dat0$date)])/sum(train0_2018$I)  ## 2018
cf_2019 = sum(dat0$severe_case[match(train0_2019$dates,dat0$date)])/sum(train0_2019$I)  ## 2019

```

## original prediction for 2020 winter flu season without COVID-19
## with "train0_combine"" 
```{r}
### poisson regression with INLA
set.seed(1992)
m.pois <- inla(I ~ logyminus_one + cumsum_yminus_over_N + gp2016 + gp2018 + gp2019 ,family = "poisson",data = train0_combine,control.predictor = list(compute=T),control.compute = list(config=T),control.fixed = list(mean=list(logyminus_one=1,default=0),prec=list(logyminus_one=100000000000)))
summary(m.pois)

############################# predict 2020 winter flu season #####################
##################  mean   ############################
new_dat0 = train0_combine[nrow(train0_combine),]   ## start from week 8 in year 2020

new_dat0 = rbind(new_dat0,NA)
new_dat0[nrow(new_dat0),"yminus_one"] = new_dat0[nrow(new_dat0)-1,"I"]
new_dat0[nrow(new_dat0),"cumsum_yminus"] = new_dat0[nrow(new_dat0)-1,"cumsum_yminus"]+new_dat0[nrow(new_dat0),"yminus_one"]
new_dat0[nrow(new_dat0),"N"] = new_dat0$N[1]
new_dat0[nrow(new_dat0),"cumsum_yminus_over_N"] = new_dat0[nrow(new_dat0),"cumsum_yminus"]/new_dat0[nrow(new_dat0),"N"]
new_dat0[nrow(new_dat0),"logyminus_one"] = log(new_dat0[nrow(new_dat0),"yminus_one"])

for (i in 1:20){

  y0 = c(train0_combine$I,NA)
  x1 = c(train0_combine$logyminus_one,new_dat0$logyminus_one[nrow(new_dat0)])
  x2 = c(train0_combine$cumsum_yminus_over_N,new_dat0$cumsum_yminus_over_N[nrow(new_dat0)])
  x3 = c(train0_combine$gp2016,FALSE)
  x4 = c(train0_combine$gp2018,FALSE)
  x5 = c(train0_combine$gp2019,FALSE)
  
  dat0_poi = data.frame(y0,x1,x2,x3,x4,x5)
  
  m.pois00 <- inla(y0 ~ x1 + x2 + x3 + x4 + x5 ,family = "poisson",data = dat0_poi,control.predictor = list(compute=T))
  
  pred0_log = tail(m.pois00$summary.fitted.values$mean,1)   ## consider the mean of bayesian 

  new_dat0[nrow(new_dat0),"logI"] = pred0_log
  new_dat0[nrow(new_dat0),"I"] = exp(pred0_log)

  new_dat0 = rbind(new_dat0,NA)
  new_dat0[nrow(new_dat0),"yminus_one"] = new_dat0[nrow(new_dat0)-1,"I"]
  new_dat0[nrow(new_dat0),"cumsum_yminus"] = new_dat0[nrow(new_dat0)-1,"cumsum_yminus"]+new_dat0[nrow(new_dat0),"yminus_one"]
  new_dat0[nrow(new_dat0),"N"] = new_dat0$N[1]
  new_dat0[nrow(new_dat0),"cumsum_yminus_over_N"] = new_dat0[nrow(new_dat0),"cumsum_yminus"]/new_dat0[nrow(new_dat0),"N"]
  new_dat0[nrow(new_dat0),"logyminus_one"] = new_dat0[nrow(new_dat0)-1,"logI"]
}

new_dat0$row_name=seq(from = match(train0_combine[nrow(train0_combine),"I"],train0_2020$I),length.out = nrow(new_dat0)) #### start from week 8 in year 2020
new_dat0_origin_model_INLA = new_dat0


############################################################################################
################## 0.025 quantile #####################################################
new_dat0 = train0_combine[nrow(train0_combine),]   ## start from week 8 in year 2020

new_dat0 = rbind(new_dat0,NA)
new_dat0[nrow(new_dat0),"yminus_one"] = new_dat0[nrow(new_dat0)-1,"I"]
new_dat0[nrow(new_dat0),"cumsum_yminus"] = new_dat0[nrow(new_dat0)-1,"cumsum_yminus"]+new_dat0[nrow(new_dat0),"yminus_one"]
new_dat0[nrow(new_dat0),"N"] = new_dat0$N[1]
new_dat0[nrow(new_dat0),"cumsum_yminus_over_N"] = new_dat0[nrow(new_dat0),"cumsum_yminus"]/new_dat0[nrow(new_dat0),"N"]
new_dat0[nrow(new_dat0),"logyminus_one"] = log(new_dat0[nrow(new_dat0),"yminus_one"])

for (i in 1:20){

  y0 = c(train0_combine$I,NA)
  x1 = c(train0_combine$logyminus_one,new_dat0$logyminus_one[nrow(new_dat0)])
  x2 = c(train0_combine$cumsum_yminus_over_N,new_dat0$cumsum_yminus_over_N[nrow(new_dat0)])
  x3 = c(train0_combine$gp2016,FALSE)
  x4 = c(train0_combine$gp2018,FALSE)
  x5 = c(train0_combine$gp2019,FALSE)
  
  dat0_poi = data.frame(y0,x1,x2,x3,x4,x5)
  
  m.pois00 <- inla(y0 ~ x1 + x2 + x3 + x4 + x5 ,family = "poisson",data = dat0_poi,control.predictor = list(compute=T))
  
  pred0_log = tail(m.pois00$summary.fitted.values$"0.025quant",1)   ## consider the 0.025quantile of bayesian

  new_dat0[nrow(new_dat0),"logI"] = pred0_log
  new_dat0[nrow(new_dat0),"I"] = exp(pred0_log)

  new_dat0 = rbind(new_dat0,NA)
  new_dat0[nrow(new_dat0),"yminus_one"] = new_dat0[nrow(new_dat0)-1,"I"]
  new_dat0[nrow(new_dat0),"cumsum_yminus"] = new_dat0[nrow(new_dat0)-1,"cumsum_yminus"]+new_dat0[nrow(new_dat0),"yminus_one"]
  new_dat0[nrow(new_dat0),"N"] = new_dat0$N[1]
  new_dat0[nrow(new_dat0),"cumsum_yminus_over_N"] = new_dat0[nrow(new_dat0),"cumsum_yminus"]/new_dat0[nrow(new_dat0),"N"]
  new_dat0[nrow(new_dat0),"logyminus_one"] = new_dat0[nrow(new_dat0)-1,"logI"]
}

new_dat0$row_name=seq(from = match(train0_combine[nrow(train0_combine),"I"],train0_2020$I),length.out = nrow(new_dat0)) #### start from week 8 in year 2020
new_dat0_origin_model_0.025quan = new_dat0

############################################################################################
################## 0.975 quantile ####################################################
new_dat0 = train0_combine[nrow(train0_combine),]   ## start from week 8 in year 2020

new_dat0 = rbind(new_dat0,NA)
new_dat0[nrow(new_dat0),"yminus_one"] = new_dat0[nrow(new_dat0)-1,"I"]
new_dat0[nrow(new_dat0),"cumsum_yminus"] = new_dat0[nrow(new_dat0)-1,"cumsum_yminus"]+new_dat0[nrow(new_dat0),"yminus_one"]
new_dat0[nrow(new_dat0),"N"] = new_dat0$N[1]
new_dat0[nrow(new_dat0),"cumsum_yminus_over_N"] = new_dat0[nrow(new_dat0),"cumsum_yminus"]/new_dat0[nrow(new_dat0),"N"]
new_dat0[nrow(new_dat0),"logyminus_one"] = log(new_dat0[nrow(new_dat0),"yminus_one"])

for (i in 1:20){

  y0 = c(train0_combine$I,NA)
  x1 = c(train0_combine$logyminus_one,new_dat0$logyminus_one[nrow(new_dat0)])
  x2 = c(train0_combine$cumsum_yminus_over_N,new_dat0$cumsum_yminus_over_N[nrow(new_dat0)])
  x3 = c(train0_combine$gp2016,FALSE)
  x4 = c(train0_combine$gp2018,FALSE)
  x5 = c(train0_combine$gp2019,FALSE)
  
  dat0_poi = data.frame(y0,x1,x2,x3,x4,x5)
  
  m.pois00 <- inla(y0 ~ x1 + x2 + x3 + x4 + x5 ,family = "poisson",data = dat0_poi,control.predictor = list(compute=T))
  
  pred0_log = tail(m.pois00$summary.fitted.values$"0.975quant",1)   ## consider the 0.975quantile of bayesian
  
  new_dat0[nrow(new_dat0),"logI"] = pred0_log
  new_dat0[nrow(new_dat0),"I"] = exp(pred0_log)

  new_dat0 = rbind(new_dat0,NA)
  new_dat0[nrow(new_dat0),"yminus_one"] = new_dat0[nrow(new_dat0)-1,"I"]
  new_dat0[nrow(new_dat0),"cumsum_yminus"] = new_dat0[nrow(new_dat0)-1,"cumsum_yminus"]+new_dat0[nrow(new_dat0),"yminus_one"]
  new_dat0[nrow(new_dat0),"N"] = new_dat0$N[1]
  new_dat0[nrow(new_dat0),"cumsum_yminus_over_N"] = new_dat0[nrow(new_dat0),"cumsum_yminus"]/new_dat0[nrow(new_dat0),"N"]
  new_dat0[nrow(new_dat0),"logyminus_one"] = new_dat0[nrow(new_dat0)-1,"logI"]
}

new_dat0$row_name=seq(from = match(train0_combine[nrow(train0_combine),"I"],train0_2020$I),length.out = nrow(new_dat0)) #### start from week 8 in year 2020
new_dat0_origin_model_0.975quan = new_dat0

```


## Model the flu dynamic with COVID-19
```{r}
R0_1st_mean_all = NULL
ori_report_rate_all = NULL
adj_report_rate1_all = NULL
adj_report_rate2_all = NULL
Rt_all_over_p_all = NULL
prior_res0 = NULL


set.seed(1992)
for (kk in 1:500){
  print(kk)
  tscal0 = 2  ## time scale (Tc)
  
  ##  fitting poisson regression model on Phase 1
  m.pois <- inla(I ~ logyminus_one + cumsum_yminus_over_N + gp2016 + gp2018 + gp2019 ,family = "poisson",data = train0_combine,control.predictor = list(compute=T),control.fixed = list(mean=list(logyminus_one=1, default=0),prec=list(logyminus_one=100000000000)))
  
  summary(m.pois)
  
  ## inverse transform sampling to get the distribution of original report rate (Phase 1)
  gen0 = runif(1)
  nval0 = approx(cumsum(m.pois$marginals.fixed$cumsum_yminus_over_N[,2])/sum(m.pois$marginals.fixed$cumsum_yminus_over_N[,2]),m.pois$marginals.fixed$cumsum_yminus_over_N[,1],xout = gen0)$y
  ## rho
  ori_report_rate = tscal0/(nval0*-1)  ## coef for cumsum_yminus_over_N 
  ori_report_rate_all = c(ori_report_rate_all,ori_report_rate)
  
  ## inverse transform sampling for R0
  gen00 = runif(1)
  nval00 = approx(cumsum(m.pois$marginals.fixed$`(Intercept)`[,2])/sum(m.pois$marginals.fixed$`(Intercept)`[,2]),m.pois$marginals.fixed$`(Intercept)`[,1],xout = gen00)$y
  
  R0_1st_mean = exp(nval00/tscal0)  
  R0_1st_mean_all = c(R0_1st_mean_all,R0_1st_mean)
  
  R0_1st_025 = exp((m.pois$summary.fixed$"0.025quant"[1])/tscal0)
  R0_1st_975 = exp((m.pois$summary.fixed$"0.975quant"[1])/tscal0)

  
  ## to prepare for calculating the correction factor for adjusted report rate (Phase 2)
  train0_2020_second_half = train0_2020[9:11,]
  cf_2020_second_half = sum(dat0$severe_case[match(train0_2020_second_half$dates,dat0$date)])/sum(train0_2020_second_half$I)  ## 2020 second half
  cf_covid1 = cf_2020_second_half/mean(c(cf_2016,cf_2018,cf_2019))
  new_coef0 = tscal0/(ori_report_rate/cf_covid1)*(-1)
  ## adjusted reporting rate for Phase 2
  adj_report_rate1 = tscal0/((new_coef0)*-1)
  adj_report_rate1_all = c(adj_report_rate1_all,adj_report_rate1)
  
  ## to prepare for calculating the correction factor for adjusted report rate (Phase 3)
  train0_2020_second_half = train0_2020[12:14,]
  cf_2020_second_half = sum(dat0$severe_case[match(train0_2020_second_half$dates,dat0$date)])/sum(train0_2020_second_half$I)  ## 2020 second half
  cf_covid2 = cf_2020_second_half/mean(c(cf_2016,cf_2018,cf_2019))
  new_coef0 = tscal0/(ori_report_rate/cf_covid2)*(-1)
  ## adjusted reporting rate
  adj_report_rate2 = tscal0/((new_coef0)*-1)
  adj_report_rate2_all = c(adj_report_rate2_all,adj_report_rate2)
}

### calculate prior for the term cumsum_yminus_over_N_p (i.e., "x2")
f3 <- function(par){
  (qnorm(p = 0.025,mean = 2,sd = par[1]) - 2/(quantile(adj_report_rate2_all,probs = c(0.975))/mean(adj_report_rate2_all)))^2 + (qnorm(p = 0.975,mean = 2,sd = par[1]) - 2/(quantile(adj_report_rate2_all,probs = c(0.025))/mean(adj_report_rate2_all)))^2
}
prior_res0 <- optimize(f = f3,interval = c(0,1))

## the precision value of "x2" is referenced by the variance of adjusted reporting rate
prior0_prec_x2 = 1/(prior_res0$minimum^2) ## prior to incorporate the uncertainty in reporting rate
prior0_prec_x1 = 1000000000  ## precision value for "x1"

################### modeling the Phase 2
##################################    week number: 9-11
new_2020_dat0 = data.frame(train0_2020$I[9:11],train0_2020$logyminus_one[9:11],train0_2020$cumsum_yminus_over_N[9:11])
names(new_2020_dat0)=c("I","logyminus_one","cumsum_yminus_over_N")

new_2020_dat0$cumsum_yminus_over_N*train0_2020$N[1]
new_2020_dat0$cumsum_yminus_over_N_p = new_2020_dat0$cumsum_yminus_over_N
new_2020_dat0$cumsum_yminus_over_N_p[1] = new_2020_dat0$cumsum_yminus_over_N[1]/mean(ori_report_rate_all)
new_2020_dat0$cumsum_yminus_over_N_p[2] = new_2020_dat0$cumsum_yminus_over_N_p[1] + new_2020_dat0$I[1]/(train0_2020$N[1]*mean(adj_report_rate1_all))
new_2020_dat0$cumsum_yminus_over_N_p[3] = new_2020_dat0$cumsum_yminus_over_N_p[2] + new_2020_dat0$I[2]/(train0_2020$N[1]*mean(adj_report_rate1_all))

new_2020_dat0$logyminus_one_over_p = new_2020_dat0$logyminus_one
new_2020_dat0$logyminus_one_over_p[1] =  new_2020_dat0$logyminus_one[1] - log(mean(ori_report_rate_all))
new_2020_dat0$logyminus_one_over_p[2] =  new_2020_dat0$logyminus_one[2] - log(mean(adj_report_rate1_all))
new_2020_dat0$logyminus_one_over_p[3] =  new_2020_dat0$logyminus_one[3] - log(mean(adj_report_rate1_all))

new_2020_dat0$I_over_p = round(new_2020_dat0$I/mean(adj_report_rate1_all),digits = 0)

#### to prepare for the regression fit
y0 = c(new_2020_dat0$I_over_p,rep(NA,length(new_2020_dat0$I)))
x1 = rep(new_2020_dat0$logyminus_one_over_p,2)
x2 = rep(new_2020_dat0$cumsum_yminus_over_N_p,2)
dat0_poi = data.frame(y0,x1,x2)

m.pois_new <- inla(y0 ~ x1 + x2  ,family = "poisson",data = dat0_poi,control.predictor = list(compute=T),control.fixed = list(mean=list(x1=m.pois$summary.fixed$mean[2], x2=-tscal0, default=0),prec=list(x1=prior0_prec_x1, x2=prior0_prec_x2))) 

summary(m.pois_new)
m.pois_new_second = m.pois_new

## new R0 for Phase 2
R0_2nd_mean = exp((m.pois_new_second$summary.fixed$mean[1])/tscal0)
R0_2nd_025 = exp((m.pois_new_second$summary.fixed$`0.025quant`[1])/tscal0)
R0_2nd_975 = exp((m.pois_new_second$summary.fixed$`0.975quant`[1])/tscal0)


################## modeling the Phase 3
##################################    week number: 12-14
### prepare training data from wk 12-14 since the reporting rate in cumsum is different
new_2020_dat0 = data.frame(rbind(new_2020_dat0, NA))
new_2020_dat0 = data.frame(rbind(new_2020_dat0, NA))
new_2020_dat0 = data.frame(rbind(new_2020_dat0, NA))

new_2020_dat0$I[4:6] = train0_2020$I[12:14]
new_2020_dat0$logyminus_one[4:6] = log(new_2020_dat0$I[3:5])

for (i in 4:4){
  new_2020_dat0$cumsum_yminus_over_N[i] = new_2020_dat0$cumsum_yminus_over_N[i-1] + (new_2020_dat0$I[i-1]/train0_2020$N[1])
  new_2020_dat0$cumsum_yminus_over_N_p[i] = new_2020_dat0$cumsum_yminus_over_N_p[i-1] + (new_2020_dat0$I[i-1]/(train0_2020$N[1]*mean(adj_report_rate1_all)))
  new_2020_dat0$logyminus_one_over_p[i] = log(exp(new_2020_dat0$logyminus_one[i])/mean(adj_report_rate1_all))
  new_2020_dat0$I_over_p[i] = round(new_2020_dat0$I[i]/mean(adj_report_rate2_all),digits = 0)
  # print(i)
}
for (i in 5:6){
  new_2020_dat0$cumsum_yminus_over_N[i] = new_2020_dat0$cumsum_yminus_over_N[i-1] + (new_2020_dat0$I[i-1]/train0_2020$N[1])
  new_2020_dat0$cumsum_yminus_over_N_p[i] = new_2020_dat0$cumsum_yminus_over_N_p[i-1] + (new_2020_dat0$I[i-1]/(train0_2020$N[1]*mean(adj_report_rate2_all)))
  new_2020_dat0$logyminus_one_over_p[i] = log(exp(new_2020_dat0$logyminus_one[i])/mean(adj_report_rate2_all))
  new_2020_dat0$I_over_p[i] = round(new_2020_dat0$I[i]/mean(adj_report_rate2_all),digits = 0)
}


y0 = c(tail(new_2020_dat0$I_over_p,3),rep(NA,length(tail(new_2020_dat0$I,3))))
x1 = rep(tail(new_2020_dat0$logyminus_one_over_p,3),2)
x2 = rep(tail(new_2020_dat0$cumsum_yminus_over_N_p,3),2)
dat0_poi = data.frame(y0,x1,x2)


m.pois_new <- inla(y0 ~ x1 + x2  ,family = "poisson",data = dat0_poi,control.predictor = list(compute=T),control.fixed = list(mean=list(x1=m.pois$summary.fixed$mean[2], x2=-tscal0, default=0),prec=list(x1=prior0_prec_x1, x2=prior0_prec_x2))) 
summary(m.pois_new)

m.pois_new_third = m.pois_new

## new R0 for Phase 3
R0_3rd_mean = exp((m.pois_new_third$summary.fixed$mean[1])/tscal0)
R0_3rd_025 = exp((m.pois_new_third$summary.fixed$`0.025quant`[1])/tscal0)
R0_3rd_975 = exp((m.pois_new_third$summary.fixed$`0.975quant`[1])/tscal0)


## prepare Rt data
## prepare cumsum_yminus_over_N_p and yminus_one
dat0_for_Rt = train0_2020[1:9,]
dat0_for_Rt$cumsum_yminus_over_N_p = dat0_for_Rt$cumsum_yminus_over_N/mean(ori_report_rate_all)
for (i in 10:(nrow(train0_2020)+1)){
  dat0_for_Rt = rbind(dat0_for_Rt,NA)
}
dat0_for_Rt$I[10:nrow(train0_2020)] = train0_2020$I[10:nrow(train0_2020)]
for (i in 10:12){
  dat0_for_Rt$cumsum_yminus_over_N_p[i] = dat0_for_Rt$cumsum_yminus_over_N_p[i-1] + (dat0_for_Rt$I[i-1]/(dat0_for_Rt$N[1]*mean(adj_report_rate1_all)))  
  dat0_for_Rt$yminus_one[i] = dat0_for_Rt$I[i-1]
}
for (i in 13:15){
  dat0_for_Rt$cumsum_yminus_over_N_p[i] = dat0_for_Rt$cumsum_yminus_over_N_p[i-1] + (dat0_for_Rt$I[i-1]/(dat0_for_Rt$N[1]*mean(adj_report_rate2_all)))  
  dat0_for_Rt$yminus_one[i] = dat0_for_Rt$I[i-1]
}
row.names(dat0_for_Rt)=NULL
dat0_for_Rt = dat0_for_Rt[-1,]    ## delete the first row to match the Rt, i.e. Rt is to predict I(t+1)

## Rt at Phase 1, 2020 (i.e., original)
Rt_first = (mean(R0_1st_mean_all)*(1-c(train0_combine$cumsum_yminus_over_N[train0_combine$gp2020==1][-1]/mean(ori_report_rate_all))))^tscal0
Rt_first_025 = (R0_1st_025*(1-c(train0_combine$cumsum_yminus_over_N[train0_combine$gp2020==1][-1]/mean(ori_report_rate_all))))^tscal0
Rt_first_975 = (R0_1st_975*(1-c(train0_combine$cumsum_yminus_over_N[train0_combine$gp2020==1][-1]/mean(ori_report_rate_all))))^tscal0

## Rt at Phase 2, 2020
Rt_second = (c(rep(R0_2nd_mean,3),rep(R0_3rd_mean,4))*(1-dat0_for_Rt$cumsum_yminus_over_N_p[8:14]))^tscal0  ## starting from week 8 Rt (t=8)
Rt_second_025 = (c(rep(R0_2nd_025,3),rep(R0_3rd_025,4))*(1-dat0_for_Rt$cumsum_yminus_over_N_p[8:14]))^tscal0  
Rt_second_975 = (c(rep(R0_2nd_975,3),rep(R0_3rd_975,4))*(1-dat0_for_Rt$cumsum_yminus_over_N_p[8:14]))^tscal0  ## starting from week 8 Rt (t=8)


Rt_all_over_p = c(Rt_first,Rt_second)
Rt_all_over_p_025 = c(Rt_first_025,Rt_second_025)
Rt_all_over_p_975 = c(Rt_first_975,Rt_second_975)

Rt_all_over_p = sqrt(Rt_all_over_p)  ### tscal0 = 2
Rt_all_over_p_025 = sqrt(Rt_all_over_p_025)
Rt_all_over_p_975 = sqrt(Rt_all_over_p_975)

Rt_all_over_p_all = rbind(Rt_all_over_p,Rt_all_over_p_025,Rt_all_over_p_975)



```




## description about the flow of model fitting
- fitting Phase 1 by poisson regression
- get the distribution of original reporting rate using inverse transform sampling based on the marginal distribution of "cumsum_yminus_over_N"
- calculate the distribution of adjusted reporting rate for Phase 2 and 3
- get distribution of R0 in Phase 1 using inverse transform sampling based on the marginal distribution of "intercept"

-	Using the distribution of reporting rate, estimate the precision parameter to be input in INLA model when regressing on phase 2 and phase 3
- regress on phase 2 and phase 3 cases through INLA with pre-set precision value







